%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Bryan Matsuo
% Modified from Kamil K Wojcicki's resume template
%   http://linux.dsplabs.com.au/resume-writing-example-latex-template-linux-curriculum-vitae-professional-cv-layout-format-text-p54/.
\documentclass[margin,line]{resume}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Bryan Matsuo}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    %Signal Processing Laboratory   \hfill office: +61 7 3735 3754          \vspace{0mm}\\\vspace{0mm}%
    157 Franklin St \#44            \hfill mobile: +1 801 671 2514         \vspace{0mm}\\\vspace{0mm}%
    Santa Cruz, CA 95060            \hfill e-mail: bryan.matsuo@gmail.com   \vspace{0mm}\\\vspace{-4.5mm}%
                                    \hfill github: https://github.com/bmatsuo   \vspace{0mm}\\\vspace{-4.5mm}%


    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Objective}

    Help develop cutting edge, scalable backend services with a team of talented people, developing my skills and
    tackling hard problems.


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{University of California, Santa Cruz} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Doctor of Computer Science} \hfill \textbf{ September 2010 -- present}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{mylist}
        %\item \textbf{Advisor:} Manfred Warmuth
        %\item \textbf{Focus:} Machine learning and satisfiability (SAT).
        \item Submitted SAT solvers EBMiniSAT and EBGlucose to SAT Competition 2011.
            The former placing 4th in number of satisfiable industrial problem instances solved.
            Expect to complete graduate program after leave of absense.
    \end{mylist}\vspace{-1.5mm}
    \textsl{BS Computer Science, BA Mathematics} \hfill \textbf{September 2004 -- March 2009}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{mylist}
        \item Honors in Computer Science
        \item Highest Honors in Mathematics
    \end{mylist}

    %__________________________________________________________________________________________________________________
    % Work Experience
    \section{\mysidestyle Work Experience}

    \textbf{LEEPS, University of California, Santa Cruz} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Developer} \hfill \textbf{April 2011 -- July 2011}\\
    Developed an open source, network-multiplayer game framework
    for academic use in experimental economics, along with lead
    James Pettit. Main responsibilities included designing an
    extensible JSON protocol, backend framework testing, evaluating
    and testing GUI toolkits for the framework, writing and fully
    documenting complete tutorial experiments using the framework,
    WxPython, and Matplotlib.

    \textbf{David Haussler \& Dimitris Achlioptas, University of California, Santa Cruz} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Research Assistant} \hfill \textbf{July 2009 -- September 2010}\\
    Developed and analyzed high-level models for quantifying/estimating
    the cumulative genetic diversity aggregated throughout mammalian
    evolution. Ran C++ simulations on a Linux cluster PBS. Analyzed
    results using Gnuplot.

    \textbf{Department of Computer Science, Univerity of California, Santa Cruz} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Grader -- Algorithms and Abstract Data Types} \hfill \textbf{March 2011 -- May 2011}\\
    \vspace{0mm}    \hfill \textbf{March 2010 -- May 2010}\\
    Responsibilities included scoring assignments and exams, as well as
    typesetting solutions with \LaTeXe and creating figures for illustration
    using PSTricks.

    \textsl{Teaching Assistant -- Introduction to Analysis of Algorithms} \hfill \textbf{January 2007 -- March 2007}\\
    Responsibilites were maintaining an active and helpful presence
    on the class mailing list, providing personalized and informative
    feedback on difficult assignments, and holding frequent discussion
    sections with students who wanted to further discuss the course
    topics.

    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Technical Skills} 

    C/C++, Go, Lisp/Scheme, Ocaml,
    Linux shell scripting (Bash, Sed, Awk, etc.),
    Perl, Python, Java, Ruby, Rails, Cluster PBS,
    SQL Databases (Postgres, SQLite),
    NoSQL Databases (Redis, MongoDB),
    \LaTeXe, Matlab/Matplotlib, Git, Github,
    Mercurial.

    %__________________________________________________________________________________________________________________
    % Other interests
    \section{\mysidestyle Interests} 

    Developing tools and automation workflows for home-entertainment system PCs, improving their integration with satellite devices (laptops, iDevices, etc.). \vspace{1mm}\\%
    Learning programming languages (currently Go), exploring different problem solving mindsets and paradigms, and finding the best tools for different problems. \vspace{1mm}\\%
    Critical examination of popular culture/media. \vspace{1mm}\\%
    Hiking/Backpacking/Walking. \vspace{1mm}\\%

    %__________________________________________________________________________________________________________________
    % Referees
%    \section{\mysidestyle Referees} 
%    {\sl Available on request.}



%______________________________________________________________________________________________________________________
%\section{\mysidestyle Referees} 
%
%\begin{tabular}{@{}p{6cm}p{6cm}}
%\textbf{Professor Kuldip Paliwal}       &  \textbf{Dr Stephen So}                   \\
%Professor                               &  Associate Lecturer                       \\
%Griffith University                     &  Griffith University                      \\
%Nathan, Queensland, Australia           &  Gold Coast, Queensland, Australia        \\
%phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
%e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
%\end{tabular}
%
%\begin{tabular}{@{}p{6cm}p{6cm}}
%\textbf{Dr Conrad Sanderson}            &  \textbf{Mr Sean Loye}                    \\
%Researcher                              &  Systems Engineer                         \\
%National ICT Australia                  &  Hewlett Packard                          \\
%St Lucia, Queensland, Australia         &  Milton, Queensland, Australia            \\
%phone: \textsl{available on request}    &  phone: \textsl{available on request}     \\
%e-mail: \textsl{available on request}   &  e-mail: \textsl{available on request}    \\
%\end{tabular}

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

